### 2020-04-18 system-model.tex
:pencil: Phase problem

\begin{section}{Problem Formulation}
	In this section, we first define the weighted sum rate-energy (WSR-E) region then formulate waveform and IRS optimization problems.
	\begin{subsection}{Weighted Sum Rate-Energy Region}
		We define the achievable WSR-E region as
		\begin{equation}
			\begin{split}
				C_{R-I}(P)
				&\triangleq \biggl\{(R,I):R\le\sum_{k=1}^K{u_{I,k}R_k},I\le\sum_{k=1}^K u_{P,k}z_k,\\
				&\quad \frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P}){\le}P\biggr\}
				% &\quad \frac{1}{2}\left(\Vert{\boldsymbol{W}_I}\Vert_F^2+\Vert{\boldsymbol{W}_P}\Vert_F^2\right){\le}P\biggr\}
			\end{split}
		\end{equation}
		where $u_{I,k},u_{P,k}$ denote the information and power weight of user $k$.
	\end{subsection}
\end{section}

>>>>

\begin{section}{Problem Formulation}
	In this section, we first define the weighted sum rate-energy (WSR-E) region then formulate waveform and IRS optimization problems.
	\begin{subsection}{Weighted Sum Rate-Energy Region}
		We define the achievable WSR-E region as
		\begin{equation}
			\begin{split}
				C_{R-I}(P)
				&\triangleq \biggl\{(R,I):R\le\sum_{k=1}^K{u_{I,k}R_k},I\le\sum_{k=1}^K u_{P,k}z_k,\\
				&\quad \frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P}){\le}P\biggr\}
				% &\quad \frac{1}{2}\left(\Vert{\boldsymbol{W}_I}\Vert_F^2+\Vert{\boldsymbol{W}_P}\Vert_F^2\right){\le}P\biggr\}
			\end{split}
		\end{equation}
		where $u_{I,k},u_{P,k}$ denote the information and power weight of user $k$.
	\end{subsection}

	\begin{subsection}{Single-user optimization}
		In this section, we first characterize the rate-energy region in the single-user setup. Define $w_{I,n}=s_{I,n}e^{j{\phi}_n}$ and $w_{P,n}=s_{P,n}e^{j{\phi}_n}$, it can be observed from \ref{eq:R_k} and \ref{eq:z_k_standard} that the optimal information and power phase are matched to frequency response as
		\begin{equation}\label{eq:phi_n}
			\phi_{I,n}^\star=\phi_{P,n}^\star=-\angle{h_n}
		\end{equation}
		\ref{eq:phi_n} maximizes rate and energy simultaneously and depends on the IRS design.
	\end{subsection}
\end{section}
